### 2020-04-28 README.Rmd
Update with results for Cambridge
Heads-up @mvl22

```{r, eval=FALSE}
# general analysis of data
rsf = readRDS("rsf.Rds")
names(rsf)
rtid = readr::read_csv("~/cyipt/cyipt-server-data/malcolm/roadtypes.csv")
rsf = left_join(rsf, rtid)
rsf_spare_lane = rsf %>% filter(
  (lanespsvforward + lanesforward) > 1 |
  (lanespsvbackward + lanesbackward) > 1,
  ! grepl(pattern = "motorway", highway)
  ) 
saveRDS(rsf_spare_lane, "rsf_spare_line.Rds")

@@

# Birmingham

```{r}
roads = rsf %>% filter(region == "Birmingham", pctgov > 100)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.zoom.limits = c(13, 14)) + tm_scale_bar()
```

@@

>>>>

```{r, eval=FALSE}
# general analysis of data
rsf = readRDS("rsf.Rds")
names(rsf)
rtid = readr::read_csv("~/cyipt/cyipt-server-data/malcolm/roadtypes.csv")
rsf = left_join(rsf, rtid)
rsf_spare_lane = rsf %>% filter(
  (lanespsvforward + lanesforward) > 1 |
  (lanespsvbackward + lanesbackward) > 1,
  ! grepl(pattern = "motorway", highway)
  ) 
saveRDS(rsf_spare_lane, "rsf_spare_line.Rds")
# piggyback::pb_upload("rsf_spare_line.Rds", "cyipt/cyipt-phase-1-data")

@@

# Cambridge

```{r}
roads = rsf %>% filter(region == "Cambridge", pctgov > 400)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis")
```

@@

```{r}
roads_top = roads %>%
  filter(length > 100) %>% 
  arrange(desc(pctgov)) %>%
  slice(1:10) 
tm_shape(roads_top) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_text("name") +
  tm_view(set.zoom.limits = c(13, 14)) + tm_scale_bar()
